\begin{thebibliography}{99}

  
\bibitem{EMC_spin} EMC, A Measurement of the Spin Asymmetry and
  Determination of the Structure Function g1 in Deep Inelastic
  Muon-Proton Scatter, Phys. Lett. B 206 (1988) 364.
\bibitem{Spin_globalAnalysis} D. Floria, M. Stratmann and
  W. Vogelsang, Extraction of spin-dependent parton densities and
  their uncertainties, Phys. Review D (2009).
\bibitem{collins_2002} J. Collins, Leading twist single
  transverse-spin asymmetries: Drell-Yan and deep inelastic
  scattering, Phys. Lett. B 536 (2002) 43.
\bibitem{DYxSection} S. Arnold and A. Metz, Dilepton production from
  polarized hadron hadron collisions, (2009),
  arXiv:0809.2262v2[hep-ex].
\bibitem{Perdekamp} M. Grosse Perdekamp and F. Yuan,
  Ann. Rev. Nucl. Part. Sci. 65, 429 (2015), arXiv:1209.2803 [hep-ph].
\bibitem{Sivers} D. Sivers, Phys. Rev. D41, 83 (1990).
\bibitem{Boer-Mulders} B. Mulders, Phys. Rev. D57 (1998).
\bibitem{DY_process} I. Kenyon, The Drell-Yan process, Reports on
  Progress in Physics 45 (1982).
\bibitem{proposal} COMPASS Collaboration, COMPASS-II Proposal, (2007).
\bibitem{CollinSoperFrame} J. Collins and D. Soper, American Physical
  Society D16.
\bibitem{compassDYpaper} COMPASS Collaboration, First measurement of
  transverse-spin-dependent azimuthal asymmetries in the Drell-Yan
  process, (2017), arXiv:1704.00488 [hep-ex].
\bibitem{compassSpec} COMPASS Collaboration, The COMPASS Experiment at
  CERN, (2007), arXiv:0703049 [hep-ex].
\bibitem{matrix_inv} V. Blodel, A New Method for the High Precision
  Alignment of Track Detectors, (2002).

  
\end{thebibliography}
